Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-11 emsoft-2019/experiments.tex
section 5
fix

%!TEX root = main.tex
\section{Experimental Results}
\input{table_pendulum_aircraft}
\input{table_integrator}

@@

%The second difference consists in the last two lines in Table\ref{tab:ipd}.
For the aircraft example, when $\varepsilon_Q=0.0030$, the error due to selecting the wrong region (\maxUij) 
exceeds the given value of $\Delta=0.1$ and our algorithm
needs to design a new controller (corresponding to the \texttt{else} branch in~\autoref{fig:overview}). 
The loop converges after 5 iterations (\texttt{then}
branch of the conditional) with $\Delta=0.112$. In each iteration, the value
for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.
Thus, the algorithm reduces memory demand
at the expense of slightly more disturbance for the controller. When
$\varepsilon_Q=0.0050$ the analysis converges after 4 iterations.
\eva{Does this mean that for the other settings, the loop in~\autoref{fig:overview}
is executed only once?}

@@

\autoref{tab:di} shows the results of this experiment.
We observe that our analysis scales up to 1200 controllers and 25000 hyperplanes \todo{these are not in the table!}
in a few hours.  The computed minimal uniform precision saves on average $49.8\%$ of memory
compared to a uniform $32$ bit baseline overall (for F, G, H and K together). 
Moreover, mixed-precision reduces the memory requirement by an additional
$9.6\%$ on average with respect to the minimal uniform baseline.
We further observe that relative savings remain largely constant for different 
prediction horizons.
% \autoref{tab:di} shows the stability of memory tuning in Daisy is
% constant with respect to the number of controllers or hyperplanes. This is true
% for both F, G and H, K. Indeed, the memory gain from uniform in 32bits and
% minimal uniform (\%32vU) is constant among different input values m. The same
% holds for (\%UvM).

>>>>

%!TEX root = main.tex
\section{Experimental Results}\label{sec:experiments}
\input{table_pendulum_aircraft}
\input{table_integrator}

@@

%The second difference consists in the last two lines in Table\ref{tab:ipd}.
For the aircraft example, when $\varepsilon_Q=0.0030$, the error due to selecting the wrong region (\maxUij) 
exceeds the given value of $\Delta=0.1$ and our algorithm
needs to design a new controller (corresponding to the \texttt{No} branch in~\autoref{fig:overview}). 
The loop converges after 5 iterations (\texttt{Yes}
branch of the diagram) with $\Delta=0.112$. In each iteration, the value
for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.
Thus, the algorithm reduces memory demand
at the expense of slightly more disturbance for the controller. When
$\varepsilon_Q=0.0050$ the analysis converges after 4 iterations.
\eva{Does this mean that for the other settings, the loop in~\autoref{fig:overview}
is executed only once?}

@@

\autoref{tab:di} shows the results of this experiment.
We observe that our analysis scales up to 1829 controllers and 14632 hyperplanes in a few hours.  The computed minimal uniform precision saves on average $49.8\%$ of memory
compared to a uniform $32$ bit baseline overall (for F, G, H and K together). 
Moreover, mixed-precision reduces the memory requirement by an additional
$9.6\%$ on average with respect to the minimal uniform baseline.
We further observe that relative savings remain largely constant for different 
prediction horizons.
% \autoref{tab:di} shows the stability of memory tuning in Daisy is
% constant with respect to the number of controllers or hyperplanes. This is true
% for both F, G and H, K. Indeed, the memory gain from uniform in 32bits and
% minimal uniform (\%32vU) is constant among different input values m. The same
% holds for (\%UvM).
